Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-30 paper/paper.tex
Tweaking

@@

?? Add in Glasgow2, Glasgow3, SND if we can get it to run on the larger set of instances,
maybe SAT just to have something to cite showing how bad SAT is at this.

>>>>

?? These results show our algorithm clearly beating PathLAD and VF2, except for very low choices of
timeout. Our algorithm also beats Glasgow2 and Glasgow3, despite being slightly simpler---on an
instance by instance basis, sometimes the additional inference performed by these algorithms pays
off, but in aggregate, there is no difference for longer choices of timeout, and a clear gain for
shorter choices.

@@

?? Add in SND if we can get it to run on the larger set of instances, maybe SAT just to have
something to cite showing how bad SAT is at this.
